When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-04-21 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added software versions

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[cf. @Simmons2012].
The paradigm was written and presented using *Psychopy*[@Peirce2019].
We used *R*[@RCT2020] with *R Studio*[@RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.

>>>>

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[cf. @Simmons2012].
The paradigm was written and presented using *Psychopy*[@Peirce2019].
We used *R* (Version 4.2.0)[@RCT2020] with *R Studio* (Version 2022.12.0)[@RStudioTeam2020] with the main packages *papaja* (Version 0.1.1)[@Aust2020], *afex* (Version 1.2-1)[@Singmann2021], and *BayesFactor* (Version 0.9.12-4.4)[@Morey2021] for all our analyses.
